\textbf{COMP0078 Assignment 2}

### 2022-12-13 submission.tex
remove end
revert last 2 commits

Some observations to make here are:\\

a) Both models seem to perform fairly well, even in the low-data setting.\\

b) Increating the number of known labels increases the accuracy and decreases
 the variance of the predictors.\\

c) Increasing the total number of datapoints generally increases both model accuracies,
and decreases variance. \\

d) The laplacian kernel method outperforms the vanilla inerpolation approach considerably,
on both accuracy and variance. \\

>>>>

\subsubsection{Discussions}
Both models exhibit high accuracy in all low-data settings. We see here that the vast majority of datapoints are connected only to points
of the same labelling, and that the graph is highly separated into 2 clusters.
Hence with minimal training information, both methods are able to predict with a
high degree of accuracy. For the laplacian seminorm interpolation method, this may be observed 
as its solution in the objective-minimisation form essentially describes a graph cut of minimal size, respecting
the true labels. We should note that in both of our models, the only pints that will be classified incorrectly with a 
reasonably high probability are these teal points in the diagram above.\\

b) Increasing the number of labelled datapoints generally increases the accuracy in both models.\\

c) Increasing the total number of datapoints generally decreases the error variance in the seminorm interpolation
model, but has a limited impact on the kernel interpolation model. \\

d) The laplacian kernel method outperforms the vanilla inerpolation approach considerably, in accuracy, and less so
for variance. \\
